Carbon stocks in aboveground biomass for Colombian mangroves with associated uncertainties

### 2017-06-05 Article_mangroves.tex
Update Article_mangroves.tex

\section{Methods}
\subsection{Data}
We used data from two different sources: (i) scientific articles and/or technical reports from studies developed in mangrove areas located in the Caribbean and Pacific coast of Colombia, in which above ground biomass (AGB) was quantified and; (ii) data from two inventories of carbon stocks in Cispat\'{a} bay (Colombian Caribbean coast) and M\'{a}laga bay (Colombian Pacific coast) \citep{Bolivar_inpreparation, Malaga2015}. For the first type of data, we selected only studies which included coordinates or specific location names that can be easily geolocated \citep{INVEMAR2007, Lema2007, DelaPena2010, Blanco2012}. The main difference between both data types is the scale of the information. The first data type report average AGB per location, while the second data type reports estimates per plot covering the same region  (22 permanent plots of 500 m\textsuperscript2 in Cispat\'{a} bay  and 10 in M\'{a}laga bay).

>>>>

\section{Methods}
\subsection{Data}
We used carbon data from two different sources: (i) scientific articles and/or technical reports from studies developed in mangrove areas located in the Caribbean and Pacific coast of Colombia, in which above ground biomass (AGB) was quantified and; (ii) data from two inventories of carbon stocks in Cispat\'{a} bay (Colombian Caribbean coast) and M\'{a}laga bay (Colombian Pacific coast) \citep{Bolivar_inpreparation, Malaga2015}. For the first type of data, we selected only studies which included coordinates or specific location names that can be easily geolocated \citep{INVEMAR2007, Lema2007, DelaPena2010, Blanco2012}. The main difference between both data types is the scale of the information. The first data type report average AGB per location, while the second data type reports estimates per plot covering the same region  (22 permanent plots of 500 m\textsuperscript2 in Cispat\'{a} bay  and 10 in M\'{a}laga bay).
